Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
Add running info about scale up example.

There are 327 satisfiable results, out of totally 97920 results, of
the example computed in 105384 milliseconds (~1.45 minutes).

\end{document}

>>>>

There are 327 satisfiable results, out of totally 97920 results, of
the example computed in 105384 milliseconds (~1.45 minutes), 
which was carried out on an Intel Core i7 at 2.5GHz with 16GB of RAM.

Then we found some extra states that never found when running only the subnets.
We figured out that is caused by a input mistake easily comparing it with the results on subnets.
\end{document}
